The effects of host galaxy properties on merging compact binaries detectable by LIGO

### 2016-07-12 paper/paper.tex
Fixing abstract, intro

Using detailed simulations of galaxy and chemical evolution, we demonstrate by example that galaxies with similar present-day appearance can host distinctly different
compact binary populations \jillianremark{ UPDATE}.  As an example, we demonstrate how the coalescing binary black hole population can differ by
factors of order  unity, and even binary neutron star populations differ by tens of percent.  

@@

This paper is organized as follows. 
In \S \ref{sec:sims}, we describe detailed hydrodynamical simulations of  several galaxies, including two of Milky Way-mass and two dwarfs.  Though the two Milky Way-like galaxies are morphologically similar at $z = 0$, we
show that their star formation and chemical evolution history have subtle but important differences due to their
distinctive merger histories.   To demonstrate
these differences have a significant practical impact,  in \S \ref{sec:model}, we introduce a simple,
metallicity-dependent  phenomenological model to calculate the present-day rate and mass distribution of compact binary
mergers from  a galaxy's known history.   In \S \ref{sec:results:BBH}, we use this model to demonstrate the binary black
hole (BH-BH) coalescence rate
can depend sensitively on the galaxy's assembly history, in a manner which is far from apparent from its present-day
properties. \jillianremark{ UPDATE}   We also demonstrate that even the coalescence rates of binary neutron stars (NSNS) and black hole-neutron
star (BH-NS) binaries also depend surprisingly sensitively on the assembly history of each galaxy. 
In \S~\ref{sec:Discussion} we discuss the implications of our study for the interpretation of host galaxy associations
identified via transient multmiessenger astronomy, in the short and long term.  We summarize our results in \S~ \ref{sec:conclude}.
%% In \S \ref{sec:results} we show that while these two galaxy formation models should produce comparable detectable binary neutron star
%% populations, these two scenarios could produce dramatically different populations of electromagnetically detectable
%% merging black hole-neutron star binaries. 
%

>>>>

Using detailed simulations of galaxy and chemical evolution, we determine how sensitively the compact binary populations
of galaxies   with similar
present-day appearance depend on the details of their assembly.
%% demonstrate by example that galaxies with similar present-day appearance can host distinctly different
%% compact binary populations \jillianremark{ UPDATE}.  As an example, we demonstrate how the coalescing binary black hole population can differ by
%% factors of order  unity, and even binary neutron star populations differ by tens of percent.  

@@

This paper is organized as follows. 
In \S \ref{sec:sims}, we describe detailed hydrodynamical simulations of  several galaxies, including two of Milky Way-mass and two dwarfs.  Though the two Milky Way-like galaxies are morphologically similar at $z = 0$, we
show that their star formation and chemical evolution history have subtle but important differences due to their
distinctive merger histories.   To demonstrate
these differences have a significant practical impact,  in \S \ref{sec:model}, we introduce a simple,
metallicity-dependent  phenomenological model to calculate the present-day rate and mass distribution of compact binary
mergers from  a galaxy's known history.   In \S \ref{sec:results:BBH}, we use this model to investigate  the compact
binary  coalescence rate
dependence on the galaxy's assembly history.   
%% We also demonstrate that even the coalescence rates of binary neutron stars (NSNS) and black hole-neutron
%% star (BH-NS) binaries also depend surprisingly sensitively on the assembly history of each galaxy. 
In \S~\ref{sec:Discussion} we discuss the implications of our study for the interpretation of host galaxy associations
identified via transient multmiessenger astronomy, in the short and long term.  We summarize our results in \S~ \ref{sec:conclude}.
%% In \S \ref{sec:results} we show that while these two galaxy formation models should produce comparable detectable binary neutron star
%% populations, these two scenarios could produce dramatically different populations of electromagnetically detectable
%% merging black hole-neutron star binaries. 
%
